---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# victax

<!-- badges: start -->
<!-- badges: end -->

The goal of victax is to provide Victorian Government budget data in tidy format.

## Installation

You can install the development version of ***victax*** from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("zerogetsamgow/victax")
```

## Taxation data

***victax*** converts [state taxation revenue](https://www.dtf.vic.gov.au/state-taxation-revenue) data published by the Victorian Department of Treasury and Finance in .xlsx format into tidy data.

The data, saved and exported as `victax_tbl` contains actuals from 1996-97 - the first year accrual-based "whole of government" financial statements - and budget, budget update, and pre-election budget update estimates back to the 2013-14 budget. Data for the current financial year and most recent budget is shown below.

```{r example}
library(victax)
## basic example code
head(
  victax_tbl |> 
    dplyr::filter(
      financial_year == fy::date2fy(Sys.Date())),12 
  )
```

The package builds an [interactive shiny app](https://zerogetsamgow.shinyapps.io/victax/) which can be used to explore the tax data.
